The yaq Project: \\ Standardized Software Enabling Flexible Instrumentation

### 2023-03-16 review/as-submitted-3/manuscript.tex
as submitted

\section*{References}
\bibliography{references}

>>>>

\section*{References}
%aipnum4-2.bst 2019-01-14 (MD) hand-edited version of apsrev4-1.bst
%Control: key (0)
%Control: author (8) initials jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (0) allowed
%Control: page (1) range
%Control: year (1) truncated
%Control: production of eprint (0) enabled
\begin{thebibliography}{45}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{https://doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{nid(2022)}]{nidaqmx}%
  \BibitemOpen
  \href@noop {} {\enquote {\bibinfo {title} {Getting started with
  {NI-DAQmx}},}\ }\bibinfo {howpublished}
  {\url{https://www.ni.com/en-us/support/documentation/supplemental/06/getting-started-with-ni-daqmx--main-page.html}}
  (\bibinfo {year} {2022}),\ \bibinfo {note} {accessed: 2022-10-02}\BibitemShut
  {NoStop}%
\bibitem [{scp(1999)}]{scpi}%
  \BibitemOpen
  \href@noop {} {\emph {\bibinfo {title} {Standard Commands for Programmable
  Instruments (SCPI)}}},\ \bibinfo {organization} {SCPI Consortium} (\bibinfo
  {year} {1999})\BibitemShut {NoStop}%
\bibitem [{mod(2012)}]{modbus}%
  \BibitemOpen
  \href@noop {} {\emph {\bibinfo {title} {MODBUS Application Protocol
  Specification}}},\ \bibinfo {organization} {Modbus} (\bibinfo {year}
  {2012})\BibitemShut {NoStop}%
\bibitem [{pic(2021)}]{picam}%
  \BibitemOpen
  \href@noop {} {\emph {\bibinfo {title} {PICam 5.x Programmer’s Manual}}},\
  \bibinfo {organization} {Teledyne Princeton Instruments} (\bibinfo {year}
  {2021})\BibitemShut {NoStop}%
\bibitem [{tho(2022)}]{thorlabs_apt}%
  \BibitemOpen
  \href@noop {} {\emph {\bibinfo {title} {Thorlabs Motion Controllers
  Host-Controller Communications Protocol}}},\ \bibinfo {organization}
  {Thorlabs} (\bibinfo {year} {2022})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Dalesio}, \citenamefont {Kraimer},\ and\
  \citenamefont {Kozubal}(1991)}]{DalesioLR1991a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~R.}\ \bibnamefont
  {Dalesio}}, \bibinfo {author} {\bibfnamefont {M.~R.}\ \bibnamefont
  {Kraimer}},\ and\ \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
  {Kozubal}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{EPICS}
  architecture},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
  {ICALEPCS}\ }\textbf {\bibinfo {volume} {91}} (\bibinfo {year}
  {1991})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Chaize}\ \emph {et~al.}(1999)\citenamefont {Chaize},
  \citenamefont {Götz}, \citenamefont {Meyer}, \citenamefont {Pérez},\ and\
  \citenamefont {Taurel}}]{AGotz1999TANGOA}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.-M.}\ \bibnamefont
  {Chaize}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Götz}},
  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Meyer}}, \bibinfo
  {author} {\bibfnamefont {M.}~\bibnamefont {Pérez}},\ and\ \bibinfo {author}
  {\bibfnamefont {E.}~\bibnamefont {Taurel}},\ }\bibfield  {title} {\enquote
  {\bibinfo {title} {{TANGO} - an object oriented control system based on
  {CORBA}},}\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {ICALEPCS}}}\
  (\bibinfo {year} {1999})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Weber}(2021)}]{WeberSebastien2021a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont
  {Weber}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{PyMoDAQ}: An
  open-source python-based software for modular data acquisition},}\ }\href
  {https://doi.org/10.1063/5.0032116} {\bibfield  {journal} {\bibinfo
  {journal} {Review of Scientific Instruments}\ }\textbf {\bibinfo {volume}
  {92}},\ \bibinfo {pages} {045104} (\bibinfo {year} {2021})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Bogdanowicz}\ \emph {et~al.}(2022)\citenamefont
  {Bogdanowicz}, \citenamefont {Rogers}, \citenamefont {Weber}, \citenamefont
  {{Zakv}}, \citenamefont {Pelissier}, \citenamefont {Wheeler}, \citenamefont
  {{Cxz}}, \citenamefont {Marazzi}, \citenamefont {{Eedm}},\ and\ \citenamefont
  {Galinskiy}}]{Bogdanowicz2022}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
  {Bogdanowicz}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Rogers}},
  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Weber}}, \bibinfo
  {author} {\bibnamefont {{Zakv}}}, \bibinfo {author} {\bibfnamefont
  {S.}~\bibnamefont {Pelissier}}, \bibinfo {author} {\bibfnamefont
  {J.}~\bibnamefont {Wheeler}}, \bibinfo {author} {\bibnamefont {{Cxz}}},
  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Marazzi}}, \bibinfo
  {author} {\bibnamefont {{Eedm}}},\ and\ \bibinfo {author} {\bibfnamefont
  {I.}~\bibnamefont {Galinskiy}},\ }\href
  {https://doi.org/10.5281/ZENODO.2556398} {\enquote {\bibinfo {title}
  {Instrumental: A python-based library for controlling lab hardware},}\ }
  (\bibinfo {year} {2022})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Tapping}(2021)}]{trspectrometer}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
  {Tapping}},\ }\href@noop {} {\enquote {\bibinfo {title} {{TRSpectrometer}
  documentation},}\ }\bibinfo {howpublished}
  {\url{https://trspectrometer.readthedocs.io/}} (\bibinfo {year} {2021}),\
  \bibinfo {note} {accessed: 2022-10-02}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Koerner}(2019)}]{Koerner_2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Koerner}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Instrbuilder: A
  {Python} package for electrical instrument control},}\ }\href
  {https://doi.org/10.21105/joss.01172} {\bibfield  {journal} {\bibinfo
  {journal} {Journal of Open Source Software}\ }\textbf {\bibinfo {volume}
  {4}},\ \bibinfo {pages} {1172} (\bibinfo {year} {2019})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Campagnola}, \citenamefont {Kratz},\ and\
  \citenamefont {Manis}(2014)}]{Campagnola_2014}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Campagnola}}, \bibinfo {author} {\bibfnamefont {M.~B.}\ \bibnamefont
  {Kratz}},\ and\ \bibinfo {author} {\bibfnamefont {P.~B.}\ \bibnamefont
  {Manis}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Acq4: an
  open-source software platform for data acquisition and analysis in
  neurophysiology research},}\ }\href
  {https://doi.org/10.3389/fninf.2014.00003} {\bibfield  {journal} {\bibinfo
  {journal} {Frontiers in Neuroinformatics}\ }\textbf {\bibinfo {volume} {8}}
  (\bibinfo {year} {2014}),\ 10.3389/fninf.2014.00003}\BibitemShut {NoStop}%
\bibitem [{pym(2022)}]{pymeasure}%
  \BibitemOpen
  \href@noop {} {\enquote {\bibinfo {title} {{PyMeasure}},}\ }\bibinfo
  {howpublished} {\url{https://pymeasure.readthedocs.io/}} (\bibinfo {year}
  {2022}),\ \bibinfo {note} {accessed: 2022-10-02}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Giesbrecht}\ \emph {et~al.}(2022)\citenamefont
  {Giesbrecht}, \citenamefont {Amsellem}, \citenamefont {Bauer}, \citenamefont
  {Mak}, \citenamefont {Wynne}, \citenamefont {Qin},\ and\ \citenamefont
  {Persaud}}]{Giesbrecht_2022}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Giesbrecht}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Amsellem}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Bauer}},
  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Mak}}, \bibinfo {author}
  {\bibfnamefont {B.}~\bibnamefont {Wynne}}, \bibinfo {author} {\bibfnamefont
  {Z.}~\bibnamefont {Qin}},\ and\ \bibinfo {author} {\bibfnamefont
  {A.}~\bibnamefont {Persaud}},\ }\bibfield  {title} {\enquote {\bibinfo
  {title} {Hardware-control: Instrument control and automation package},}\
  }\href {https://doi.org/10.21105/joss.02688} {\bibfield  {journal} {\bibinfo
  {journal} {Journal of Open Source Software}\ }\textbf {\bibinfo {volume}
  {7}},\ \bibinfo {pages} {2688} (\bibinfo {year} {2022})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Shkarin}(2022)}]{pylablib}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Shkarin}},\ }\href {https://doi.org/10.5281/zenodo.7324876} {\enquote
  {\bibinfo {title} {{pyLabLib}},}\ }\bibinfo {howpublished}
  {\url{https://doi.org/10.5281/zenodo.7324876}} (\bibinfo {year}
  {2022})\BibitemShut {NoStop}%
\bibitem [{Note1()}]{Note1}%
  \BibitemOpen
  \bibinfo {note} {See Supplementary Material for a full description of the
  name ``\protect \texttt {yaq}{}''}\BibitemShut {NoStop}%
\bibitem [{Note2()}]{Note2}%
  \BibitemOpen
  \bibinfo {note} {The \protect \texttt {yaq}{} protocol is fully specified by
  the set of accepted \protect \texttt {yaq}{} Enhancement Proposals at
  https://yeps.yaq.fyi/}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Raymond}(1996)}]{Raymond_1996}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~S.}\ \bibnamefont
  {Raymond}},\ }\href@noop {} {\emph {\bibinfo {title} {The new hacker’s
  dictionary}}},\ \bibinfo {edition} {3rd}\ ed.\ (\bibinfo  {publisher} {MIT
  Press},\ \bibinfo {address} {Cambridge, Mass},\ \bibinfo {year}
  {1996})\BibitemShut {NoStop}%
\bibitem [{Avr(2022)}]{AvroSpecification}%
  \BibitemOpen
  \href@noop {} {\enquote {\bibinfo {title} {Apache avro specification},}\
  }\bibinfo {howpublished}
  {\url{https://avro.apache.org/docs/1.11.1/specification/}} (\bibinfo {year}
  {2022}),\ \bibinfo {note} {accessed: 2022-10-02}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Segal}(2005)}]{SegalJudith2005a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Segal}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {When software
  engineers met research scientists: A case study},}\ }\href
  {https://doi.org/10.1007/s10664-005-3865-y} {\bibfield  {journal} {\bibinfo
  {journal} {Empirical Software Engineering}\ }\textbf {\bibinfo {volume}
  {10}},\ \bibinfo {pages} {517--536} (\bibinfo {year} {2005})}\BibitemShut
  {NoStop}%
\bibitem [{Note3()}]{Note3}%
  \BibitemOpen
  \bibinfo {note} {\protect \texttt {yaqc} available on PyPI at
  https://pypi.org/project/yaqc/}\BibitemShut {NoStop}%
\bibitem [{Note4()}]{Note4}%
  \BibitemOpen
  \bibinfo {note} {\protect \texttt {yaqc-qtpy} available on PyPI at
  https://pypi.org/project/yaqc-qtpy/}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Allan}\ \emph {et~al.}(2019)\citenamefont {Allan},
  \citenamefont {Caswell}, \citenamefont {Campbell},\ and\ \citenamefont
  {Rakitin}}]{AllanDanielB2019a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
  {Allan}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Caswell}},
  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Campbell}},\ and\
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Rakitin}},\ }\bibfield
  {title} {\enquote {\bibinfo {title} {Bluesky's ahead: A multi-facility
  collaboration for an a la carte software project for data acquisition and
  management},}\ }\href {https://doi.org/10.1080/08940886.2019.1608121}
  {\bibfield  {journal} {\bibinfo  {journal} {Synchrotron Radiation News}\
  }\textbf {\bibinfo {volume} {32}},\ \bibinfo {pages} {19--22} (\bibinfo
  {year} {2019})}\BibitemShut {NoStop}%
\bibitem [{Note5()}]{Note5}%
  \BibitemOpen
  \bibinfo {note} {\protect \texttt {yaqc-bluesky} available on PyPI at
  https://pypi.org/project/yaqc-bluesky/}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Mukamel}(2000)}]{MukamelShaul2000a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Mukamel}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
  {Multidimensional femtosecond correlation spectroscopies of electronic and
  vibrational excitations},}\ }\href
  {https://doi.org/10.1146/annurev.physchem.51.1.691} {\bibfield  {journal}
  {\bibinfo  {journal} {Annual Review of Physical Chemistry}\ }\textbf
  {\bibinfo {volume} {51}},\ \bibinfo {pages} {691--729} (\bibinfo {year}
  {2000})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Wright}(2011)}]{WrightJohnCurtis2011a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
  {Wright}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Multiresonant
  coherent multidimensional spectroscopy},}\ }\href
  {https://doi.org/10.1146/annurev-physchem-032210-103551} {\bibfield
  {journal} {\bibinfo  {journal} {Annual Review of Physical Chemistry}\
  }\textbf {\bibinfo {volume} {62}},\ \bibinfo {pages} {209--230} (\bibinfo
  {year} {2011})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Carlson}(1988)}]{CarlsonRogerJohn1988a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
  {Carlson}},\ }\emph {\bibinfo {title} {Quantitative Aspects of High
  Resolution, Fully Resonant, Four-Wave Mixing Spectroscopy For the Analysis of
  Vibronic Mode Coupling in Molecules}},\ \href@noop {} {Ph.D. thesis},\
  \bibinfo  {school} {University of Wisconsin-Madison} (\bibinfo {year}
  {1988})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Meyer}(2004)}]{MeyerKentAlbert2004b}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~A.}\ \bibnamefont
  {Meyer}},\ }\emph {\bibinfo {title} {Frequency-Scanned Ultrafast
  Spectroscopic Techniques Applied to Infrared Four-Wave Mixing
  Spectroscopy}},\ \href@noop {} {Ph.D. thesis},\ \bibinfo  {school}
  {University of Wisconsin--Madison} (\bibinfo {year} {2004})\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Kain}(2017)}]{KainSchuyler2017a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Kain}},\ }\emph {\bibinfo {title} {Transition of Frequency-Domain Coherent
  Multidimensional Spectroscopic Methods to the Femtosecond Time Regime with
  Applications to Nanoscale Semiconductors}},\ \href@noop {} {Ph.D. thesis},\
  \bibinfo  {school} {University of Wisconsin-Madison} (\bibinfo {year}
  {2017})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Thompson}(2018)}]{ThompsonBlaiseJonathan2018a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~J.}\ \bibnamefont
  {Thompson}},\ }\emph {\bibinfo {title} {Development of Frequency Domain
  Multidimensional Spectroscopy with Applications in Semiconductor
  Photophysics}},\ \href {https://doi.org/10.5281/zenodo.7627321} {Ph.D.
  thesis},\ \bibinfo  {school} {University of Wisconsin--Madison} (\bibinfo
  {year} {2018})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Sunden}(2022)}]{SundenKyle2022}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~F.}\ \bibnamefont
  {Sunden}},\ }\emph {\bibinfo {title} {yaq: Yet Another Acquisition A modular
  approach to spectroscopy software and instrumentation}},\ \href
  {https://doi.org/10.5281/zenodo.7627331} {Ph.D. thesis},\ \bibinfo  {school}
  {University of Wisconsin--Madison} (\bibinfo {year} {2022})\BibitemShut
  {NoStop}%
\bibitem [{Note6()}]{Note6}%
  \BibitemOpen
  \bibinfo {note} {\protect \texttt {yaqd-core-python} available on PyPI at
  https://pypi.org/project/yaqd-core}\BibitemShut {NoStop}%
\bibitem [{Note7()}]{Note7}%
  \BibitemOpen
  \bibinfo {note} {\protect \texttt {yaq-traits} available on PyPI at
  https://pypi.org/project/yaq-traits}\BibitemShut {NoStop}%
\bibitem [{Note8()}]{Note8}%
  \BibitemOpen
  \bibinfo {note} {\protect \texttt {yaqd-brooks-mfc-gf} source code available
  on GitHub at \protect \texttt
  {https://github.com/yaq-project/yaqd-brooks/}}\BibitemShut {NoStop}%
\bibitem [{pys()}]{pyserial}%
  \BibitemOpen
  \href@noop {} {\enquote {\bibinfo {title} {{PySerial}},}\ }\bibinfo
  {howpublished} {\url{https://pypi.org/project/pyserial}},\ \bibinfo {note}
  {accessed: 2022-10-02}\BibitemShut {NoStop}%
\bibitem [{pyu()}]{pyusb}%
  \BibitemOpen
  \href@noop {} {\enquote {\bibinfo {title} {{PyUSB}},}\ }\bibinfo
  {howpublished} {\url{https://pypi.org/project/pyusb}},\ \bibinfo {note}
  {accessed: 2022-11-06}\BibitemShut {NoStop}%
\bibitem [{pyv()}]{pyvisa}%
  \BibitemOpen
  \href@noop {} {\enquote {\bibinfo {title} {{PyVISA}},}\ }\bibinfo
  {howpublished} {\url{https://pypi.org/project/pyvisa}},\ \bibinfo {note}
  {accessed: 2022-11-06}\BibitemShut {NoStop}%
\bibitem [{pym()}]{pymodbus}%
  \BibitemOpen
  \href@noop {} {\enquote {\bibinfo {title} {{PyModbus}},}\ }\bibinfo
  {howpublished} {\url{https://pypi.org/project/pymodbus}},\ \bibinfo {note}
  {accessed: 2022-11-06}\BibitemShut {NoStop}%
\bibitem [{Note9()}]{Note9}%
  \BibitemOpen
  \bibinfo {note} {See https://yaq.fyi/daemons/ and https://yaq.fyi/hardware/
  for living lists of all \protect \texttt {yaq}{} daemons and supported
  hardware, respectively.}\BibitemShut {Stop}%
\bibitem [{\citenamefont {Salazar}\ \emph {et~al.}(2021)\citenamefont
  {Salazar}, \citenamefont {Thompson}, \citenamefont {Knapp}, \citenamefont
  {Myers},\ and\ \citenamefont {Stahl}}]{SalazarChaseA2021a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~A.}\ \bibnamefont
  {Salazar}}, \bibinfo {author} {\bibfnamefont {B.~J.}\ \bibnamefont
  {Thompson}}, \bibinfo {author} {\bibfnamefont {S.~M.~M.}\ \bibnamefont
  {Knapp}}, \bibinfo {author} {\bibfnamefont {S.~R.}\ \bibnamefont {Myers}},\
  and\ \bibinfo {author} {\bibfnamefont {S.~S.}\ \bibnamefont {Stahl}},\
  }\bibfield  {title} {\enquote {\bibinfo {title} {Multichannel
  gas-uptake/evolution reactor for monitoring liquid-phase chemical
  reactions},}\ }\href {https://doi.org/10.1063/5.0043007} {\bibfield
  {journal} {\bibinfo  {journal} {Review of Scientific Instruments}\ }\textbf
  {\bibinfo {volume} {92}},\ \bibinfo {pages} {044103} (\bibinfo {year}
  {2021})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Allman}(2012)}]{Allman_2012}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
  {Allman}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Managing
  technical debt},}\ }\href {https://doi.org/10.1145/2160718.2160733}
  {\bibfield  {journal} {\bibinfo  {journal} {Communications of the ACM}\
  }\textbf {\bibinfo {volume} {55}},\ \bibinfo {pages} {50--55} (\bibinfo
  {year} {2012})}\BibitemShut {NoStop}%
\bibitem [{Note10()}]{Note10}%
  \BibitemOpen
  \bibinfo {note} {\protect \texttt {yaqd-fakes} available on PyPI at
  https://pypi.org/project/yaqd-fakes/}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Segal}(2007)}]{SegalJudith2007a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Segal}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Some problems of
  professional end user developers},}\ }in\ \href
  {https://doi.org/10.1109/vlhcc.2007.17} {\emph {\bibinfo {booktitle} {{IEEE}
  Symposium on Visual Languages and Human-Centric Computing ({VL}/{HCC}
  2007)}}}\ (\bibinfo  {publisher} {{IEEE}},\ \bibinfo {year}
  {2007})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Cohen}\ \emph {et~al.}(2021)\citenamefont {Cohen},
  \citenamefont {Katz}, \citenamefont {Barker}, \citenamefont {Hong},
  \citenamefont {Haines},\ and\ \citenamefont {Jay}}]{CohenJeremy2021a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Cohen}}, \bibinfo {author} {\bibfnamefont {D.~S.}\ \bibnamefont {Katz}},
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Barker}}, \bibinfo
  {author} {\bibfnamefont {N.~C.}\ \bibnamefont {Hong}}, \bibinfo {author}
  {\bibfnamefont {R.}~\bibnamefont {Haines}},\ and\ \bibinfo {author}
  {\bibfnamefont {C.}~\bibnamefont {Jay}},\ }\bibfield  {title} {\enquote
  {\bibinfo {title} {The four pillars of research software engineering},}\
  }\href {https://doi.org/10.1109/ms.2020.2973362} {\bibfield  {journal}
  {\bibinfo  {journal} {IEEE Software}\ }\textbf {\bibinfo {volume} {38}},\
  \bibinfo {pages} {97--105} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Nowogrodzki}(2019)}]{NowogrodzkiAnna2019a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Nowogrodzki}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {How to
  support open-source software and stay sane},}\ }\href
  {https://doi.org/10.1038/d41586-019-02046-0} {\bibfield  {journal} {\bibinfo
  {journal} {Nature}\ }\textbf {\bibinfo {volume} {571}},\ \bibinfo {pages}
  {133--134} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
\end{thebibliography}%
